---
title: "HackeRnews - specification"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{HackeRnews - specifiation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# Hacker News

  The `hackeRnews` package was created in order to simplify the process of getting data from [Hacker News](https://news.ycombinator.com/news). Hacker News is a user-generated content website that focuses on stories related to computer science. The website is composed of user submitted stories where each one provides a link to the original data source. Moreover, users have the ability to upvote a story if they have found it interesting. Each story contains a comment section which allows users to discuss about the presented subject. Besides news stories Hacker News contains the following sections:

- 'Ask' section where users can ask questions to the Hacker News community
- 'Show' section where users can share something that they have created
- 'Jobs' section where users can browse job offers

# Hacker News API

The Hacker News API official documentation can be found [here](https://github.com/HackerNews/API). The API serves data in JSON format. The `hackeRnews` package allows the retrieve this data in form of convenient R objects. Each object (story, comment, ...) has a unique id and can be retrieved using this id. The API also provides a way to fetch up to 500 top and new stories, latest best stories, ask stories, show stories and job stories. 

Examples of using the `hackeRnews` package to retrieve data from the official Hacker News API are presented below:

## hackeRnews usage

```{r warn=FALSE}
library(hackeRnews)
```

### news stories

To fetch best/new/top stories the user can use the `get_*_stories` function. Each function takes one optional argument `max_items` that limits the number of returned stories. 

For example to fetch the top 5 best stories:

```{r}
best_stories <- get_best_stories(max_items=5)
best_stories[[1]]
```

There is a method that allows to fetch just raw ids of best/new/top stories as well `get_*_stories_ids()`

```{r}
best_stories_ids <- get_best_stories_ids()
best_stories_ids[1:5] # output truncated for legibility
```

### ask / job / show stories

Similar to news stories. There are `get_latest_*_stories` that returns latest * stories and  `get_latest_*_stories_ids` that returns latest * stories ids.

For example to fetch the 3 latest ask stories:

```{r}
ask_stories <- get_latest_ask_stories(max_items=3)
ask_stories[[1]]
```


### comments
The discussion in story threads is represented as system of comments. Each story has top level comments ids stored under the `kids` property. Each comment post can have it's own set of comments ids under `kids` property (sub-comments) and so on. In order to retrieve all of the comments of a specific story, just use the `get_comments` function.

```{r}
top_story <- get_top_stories(max_items=1)[[1]]
get_comments(top_story)
```

### user

To fetch data about user 'jl' just use the `get_user_by_username` function:

```{r}
user <- get_user_by_username('jl')
user
```

### all items / latest items

It's possible to iterate over latest items by fetching the id of the latest item by using the `get_max_item_id` function and then walking backwards to discover latest items. Using that method it's possible to fetch all items on Hacker News.

For example to fetch 10 latest items:

```{r eval=FALSE}
max_item_id <- get_max_item_id()
latest_items <- get_items_by_ids(seq(max_item_id, max_item_id - 10))
```

### updates

Latest items and profile changes can be retrieved using `get_updates`

```{r}
updates <- get_updates()
updates$profiles[1:5] # output truncated for legibility
updates$items[1:5]    # output truncated for legibility
```
