---
title: "HackeRnews - specifiation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{HackeRnews - specifiation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(hackeRnews)
```


# Hacker News

`hackeRnews` package was created to simplify getting data from [Hacker News](https://news.ycombinator.com/news). Hacker News is a user-generated content website that focuses on stories related to computer science. Website serves list of user submitted stories. Each story provides link to original data source. Users have ability to upvote story if they found it useful. Every story have also comment section that allow users to create dicussion using comments system. Beside news stories websites has also:

- 'Ask' section where user can seek answers for own questions among HackerNew's community
- 'Show' section where user can share something on what he/she made
- 'Jobs' section where user can browse job offers

# Hacker News API

Hacker News API official documentation can be found [here](https://github.com/HackerNews/API). API serves data in JSON format, `hackeRnews` package transforms some properties into more friendly types, e.g. unixtimestamp to `POSIXct`. Each object (story, comment, ...) has unique id and can be retrieved by that id. API also provides way to fetch up to 500 top and new stories, latest best stories, ask stories, show stories and job stories. 

Below are examples that shows how to use `hackeRnews` to retrieve data from API.

## Hacker News items

All items (stories, comments, ...) have some of the following properties:

| Property Name | Type | Description  |
| :-- | :-: | --------------- |
| by | chr | The username of the item's author | 
| descendants | int | In the case of stories or polls, the total comment count. |
| id  | chr | The item's unique id |
| kids | int[] | The ids of the item's comments, in ranked display order  | 
| parent | chr | The comment's parent: either another comment or the relevant story |
| score | int | The story's score |
| text | chr | The comment, story or poll text. HTML.
| time | POSIXct | Creation date of the item | 
| title | chr | The title of the story |
| type | chr  | The type of item. One of "job", "story", "comment", "poll", or "pollopt" | 
| url | chr | The URL of the story | 

## hackeRnews usage


### news stories

To fetch best/new/top stories user can use `hackeRnews::get_*_stories` method. Each method takes one optional argument `max_items` that limits number of returned stories. 

For example to fetch 5 best stories:

```{r}
best_stories <- hackeRnews::get_best_stories(max_items=5)
best_stories[[1]]
```

Also there is method to fetch just raw ids of best/new/top stories `hackeRnews::get_*_stories_ids()`

```{r}
best_stories_ids <- hackeRnews::get_best_stories_ids()
best_stories_ids[1:5] # output limited to 5 items for legibility
```

